\vspace{-2cm}Formation Control of AAUSHIP

### 2015-04-12 paper.tex
JAL: minor updates
JAL: Shrinked to 7 pages
Fix fig caption and papersize

%\documentclass[a4paper,12pt]{IEEEtran}
\documentclass[conference]{IEEEtran}
%\input{preamble}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage[utf8]{inputenc} % So we can input Nicks name in the paper title!
\usepackage[T1]{fontenc}
\usepackage{amsmath}%,amsfonts,amssymb} % Added so we can do pretty math equations.
\usepackage{geometry}
\usepackage{lipsum}
\usepackage[pdftex,bookmarks=true,bookmarksnumbered=true]{hyperref}
\usepackage[english,final]{varioref} % Vi kan anvende \vref
\usepackage[draft]{fixme}
\usepackage[boxed,linesnumbered]{algorithm2e}
%\usepackage{glossaries}
%\setacronymstyle{long-sc-short}
\geometry{left=3cm,right=3cm,bottom=4cm}
\newcommand{\colwidth}{3in}
\begin{document}

@@

\begin{abstract}
Many maritime mapping tasks are today carried out by large research ships, which are very costly to operate. As a way to overcome this, a number of small surveying vessels have been developed called AAUSHIP. In order to efficiently map the an area with such smaller vessels, it is important that several vessels are able to corporate on the task at hand. In this paper, the developed formation control strategy for the AAUSHIP series of vessels is presented, along with simulation results, which confirms, that the algorithm works as intended.
\end{abstract}

\section{Introduction}
The background for the formation control subject of this project
originate in a collaboration with Port of Aalborg, who has a vision to
make their harbour an intelligent harbour. This will, among other
things, include autonomous piloting of cargo ships bringing cargo to and from
Aalborg. For the cargo ships to enter the harbour it is important that
the seabed is deep enough and the sand has not build up larger bars or
moved the channel unexpectedly.  Currently bathymetry surveys are
performed manually with a small manned survey boat equipped with a
multi beam sonar, scanning some area of interest, which is a smaller
fraction of the whole Limfjord.

@@

\begin{figure}[htbp]
  \includegraphics[width=\colwidth]{fig/ftotmagnfigpdf1}
	\caption{Plot of one agent's trajectory with a desired position with
		obstacles to avoid}
  \label{fig:potfieldagenti}
\end{figure}

@@

\begin{figure}[htbp]
  \includegraphics[width=\colwidth]{fig/ftotmagnfigpdf}
	\caption{Agent $i$ avoids agent $j$ and converges to the minima at
		the virtual leader}
  \label{fig:avoidagent}
\end{figure}

@@

\begin{figure}[htbp]
  \includegraphics[width=\colwidth]{fig/ftotmagnfigpdf3}
	\caption{An agent gets stuck due to a local minima between two other
	agents. The agent cannot get out of this minima unless the other two
	agents makes the space for the agent to pass through}
  \label{fig:roevproblem}
\end{figure}

@@

\begin{figure}[htbp]
  \includegraphics[width=\colwidth]{fig/ftotmagnfigpdf4}
	\caption{An agent that before was stuck now does not get into a
		local minima close to the agents, as it now sees the two other
		agents as one larger agent.}
  \label{fig:solroevproblem}
\end{figure}

@@

A simulation of the algorithm with the dynamics of the AAUSHIP can be seen on figure \ref{fig:potform}.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\colwidth]{fig/lawn-bar-formation}
  \caption{Four agents are placed relative to the middle point of the formation, the virtual leader. This leader moves at the trajectory with the waypoints, but only changes to the next waypoint if the agents are in formation.}
  \label{fig:potform}
\end{figure}
The red crosses are waypoints that have been targeted as the next waypoint to reach. The line connecting those waypoints are the virtual leader movement, which changes position from waypoint to waypoint to generate the straight line segments for the formation to follow. Every of the four agents have a relative position placement to the virtual leader, the agents positions are $p_{ij}$ and given as $p^n_{vl} + \text{offset}$ and the position of the virtual leader is given as $p^n_{vl}$. The ships are shown as yellow ships and the ships in formation is connected with a red line.

>>>>

%\documentclass[a4paper,12pt]{IEEEtran}
\documentclass[a4paper,conference]{IEEEtran}
%\input{preamble}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage[utf8]{inputenc} % So we can input Nicks name in the paper title!
\usepackage[T1]{fontenc}
\usepackage{amsmath}%,amsfonts,amssymb} % Added so we can do pretty math equations.
\usepackage{geometry}
\usepackage{lipsum}
\usepackage[pdftex,bookmarks=true,bookmarksnumbered=true]{hyperref}
\usepackage[english,final]{varioref} % Vi kan anvende \vref
\usepackage[draft]{fixme}
\usepackage[boxed,linesnumbered]{algorithm2e}
%\usepackage{glossaries}
%\setacronymstyle{long-sc-short}
\geometry{left=3cm,right=3cm,bottom=4cm}
\newcommand{\colwidth}{3in}
\begin{document}

@@

\begin{abstract}
Many maritime mapping tasks are today carried out by large research ships, which are very costly to operate. As a way to overcome this, a number of small surveying vessels have been developed called AAUSHIP. In order to efficiently map the an area with such smaller vessels, it is important that several vessels are able to corporate on the task at hand. In this paper, the developed formation control strategy for the AAUSHIP series of vessels is presented, along with simulation results, which confirms, that the algorithm works as intended.
\end{abstract}
\vspace{-3mm}
\section{Introduction}
The background for the formation control subject of this project
originate in a collaboration with Port of Aalborg, who has a vision to
make their harbour an intelligent harbour. This will, among other
things, include autonomous piloting of cargo ships bringing cargo to and from
Aalborg. For the cargo ships to enter the harbour it is important that
the seabed is deep enough and the sand has not build up larger bars or
moved the channel unexpectedly.  Currently bathymetry surveys are
performed manually with a small manned survey boat equipped with a
multi beam sonar, scanning some area of interest, which is a smaller
fraction of the whole Limfjord.

@@

\begin{figure}[htbp]
  \includegraphics[width=.9\linewidth]{fig/ftotmagnfigpdf1}
	\caption{Plot of one agent's trajectory with a desired position with
		obstacles to avoid}
  \label{fig:potfieldagenti}
\end{figure}

@@

\begin{figure}[htbp]
  \includegraphics[width=.9\linewidth]{fig/ftotmagnfigpdf}
	\caption{Agent $i$ avoids agent $j$ and converges to the minima at
		the virtual leader}
  \label{fig:avoidagent}
\end{figure}

@@

\begin{figure}[htbp]
  \includegraphics[width=.9\linewidth]{fig/ftotmagnfigpdf3}
	\caption{An agent gets stuck due to a local minima between two other
	agents. The agent cannot get out of this minima unless the other two
	agents makes the space for the agent to pass through}
  \label{fig:roevproblem}
\end{figure}

@@

\begin{figure}[htbp]
  \includegraphics[width=.9\linewidth]{fig/ftotmagnfigpdf4}
	\caption{An agent that before was stuck now does not get into a
		local minima close to the agents, as it now sees the two other
		agents as one larger agent.}
  \label{fig:solroevproblem}
\end{figure}

@@

A simulation of the algorithm with the dynamics of the AAUSHIP can be seen on figure \ref{fig:potform}.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\colwidth]{fig/lawn-bar-formation}
  \caption{Four agents are placed relative to the middle point of the
	formation, the virtual leader. This leader moves at the trajectory
with the waypoints, but only changes to the next waypoint if the
agents are in formation. The blue circles with the red plus signs are
the waypoints of the virtual leader. The other paths are computed from
this and the FRP.}
  \label{fig:potform}
\end{figure}
The red crosses are waypoints that have been targeted as the next waypoint to reach. The line connecting those waypoints are the virtual leader movement, which changes position from waypoint to waypoint to generate the straight line segments for the formation to follow. Every of the four agents have a relative position placement to the virtual leader, the agents positions are $p_{ij}$ and given as $p^n_{vl} + \text{offset}$ and the position of the virtual leader is given as $p^n_{vl}$. The ships are shown as yellow ships and the ships in formation is connected with a red line.
